\thesistitle

### 2019-07-22 sections/experimentalsetup.tex
Fixed stuff
OKay this is harder than I thought

\begin{figure}[H]
    \includegraphics[width=0.6\columnwidth]{img/context}
    \caption{Abstract representation of clone classes and clone instances.}
  \label{fig:clonecontext}
\end{figure}

@@

\begin{figure}[H]
  \caption{Abstract figure displaying relations of clone classes. Arrows represent superclass relations.}
    \medskip
    \includegraphics[width=1\columnwidth]{img/Relation}
  \label{fig:clonerelation}
\end{figure}

@@

@@

A clone class is flagged as ``Same method'' if all clone instances in the clone class are in the same method:

\begin{equation}\label{eq:samemethod}
\forall (i_1 \in C) \forall (i_2 in C) Mi_1 = Mi_2
\end{equation}

Where \textit{M} is the method in which a clone instance is found. Please note that a clone instance may not always be in a method, for which this predicate will fail. Each node in a clone instance is checked for this predicate, so if a single node of a clone instance is outside a method, the predicate will fail.

A clone class is flagged as ``Same class'' if all clone instances in the clone class are in the same class:

\begin{equation}\label{eq:samemethod}
\forall (i_1 \in C) \forall (i_2 in C) Di_1 = Di_2
\end{equation}

Where \textit{D} is the class declaration in which the clone instance is found.

@@

>>>>

\begin{figure}[H]
  \centering
    \includegraphics[width=0.8\columnwidth]{img/context}
    \caption{Abstract representation of clone classes and clone instances.}
  \label{fig:clonecontext}
\end{figure}

@@

\begin{figure}[H]
  \centering
    \includegraphics[width=0.6\columnwidth]{img/Relation}
      \caption{Abstract figure displaying relations of clone classes. Arrows represent superclass relations.}
  \label{fig:clonerelation}
\end{figure}

@@

To check a the relation for a given clone class, we compare each node in a clone instance with the respective nodes in each other clone instance within a clone class. So for a clone class with x clone instances and each clone instance has y nodes, we perform:

\begin{equation}\label{eq:sameclass}
((x)(x + 1) / 2) * y
\end{equation}

comparisons to determine the relation. Each of these checks will result in one of the relations from the list above. Of these relations, the item lowest in the list is going to be the relation of the clone class. So for instance, if a clone class has 15 nodes that denote a \textit{Superclass} relation but 3 nodes are \textit{Unrelated}, the clone class becomes \textit{Unrelated}.

@@

A clone class is flagged as ``Same method'' if all clone instances in the clone class are in the same method. We check this relation for each node in a clone instance with each other node in each other clone instance within a clone class. We define the method as the first method declaration that is found when tracing  from a node in the clone instance. Please note that a clone instance may not always be in a method, for which this predicate will fail. Each node in a clone instance is checked for this predicate, so if a single node of a clone instance is outside a method, the predicate will fail.

A clone class is flagged as ``Same class'' if all clone instances in the clone class are in the same class. We define the class as the first class declaration that is encountered when following the parent nodes in the ast for a given cloned node.

@@

\begin{equation}\label{eq:sameclass}
\forall (i_1 \in C)\text{ }\forall (i_2 \in C)\text{ }Si_1 = Di_2 \lor Si_2 = Di_1
\end{equation}

Where\
